The promise of community-driven preprints in ecology and evolution

### 2024-05-10 ms/ms.qmd
Update authors next in line

Authors: Daniel W.A. Noble ^1^, $\ddagger$, Hackathon Participants, Shinichi Nakagawa^2,\*^,Malgorzata Lagisz^2,\*^

@@

Here, we explore the first 1000+ preprints uploaded to *EcoEvoRxiv* to understand preprint practices and uses in ecology and evolution. We focus our attention on better understanding: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender impact preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published. In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further educate researchers about the benefits of using community-driven preprint servers to post their research findings.

>>>>

Authors: Daniel W.A. Noble ^1^, $\ddagger$, Zoe A. Xirocostas, Nicholas C. Wu, April R. Martinig, Shinichi Nakagawa^2,\*^,Malgorzata Lagisz^2,\*^

@@

Here, we explore the first 1000+ preprints uploaded to *EcoEvoRxiv* to understand preprint practices and uses in ecology and evolution. We focus our attention on better understanding: 1) in what countries authors who use *EcoEvoRxiv* are located; 2) how career stage and gender are associated with preprint server use; 3) the extent to which authors make use of preprint servers for registered reports and community-driven peer review; 4) the extent to which data and code are shared in preprints; and 5) how many preprints remain unpublished, and for those that are published, how long it took them to become published. In the process, we also provide a summary of what makes *EcoEvoRxiv* distinct from other preprint servers to help further educate researchers about the benefits of using community-driven preprint servers to post their research findings.
